A Non-local Bayesian Video Denoising Method

### 2015-12-10 doc/201511_report_plein-phare/report_plein-phare.tex
[doc] Report Plein-Phare

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[10pt, journal, twocolumn, final, a4paper]{IEEEtran}
%
\usepackage{makeidx}  % allows for indexgeneration
%

% allow for compress references ranges (IEEEtran_HOWTO S.VII)
% noadjust removes a leading space before the []
\usepackage[noadjust]{cite}

@@

%\usepackage[left=1.2in,right=1.2in]{geometry}

@@

% pablo's commands for comments and suggested modifications
\newcommand{\pa}[1]{\textcolor{cyan}{#1}}
\newcommand{\psub}[2]{\pa{\sout{#1}}\pa{/#2}}
\newcommand{\prm}[1]{\pa{\sout{#1}}}
\newcommand{\padd}[1]{\pa{#1}}
%\newcommand{\pcomment}[1]{\textit{\pa{#1}}}
\newcommand{\pcomment}[1]{}

@@

@@

\title{A Non-local Bayesian Video Denoising Method}

\author{Pablo~Arias, Jean-Michel~Morel%
\thanks{P. Arias (\texttt{pablo.arias@cmla.ens-cachan.fr}) and J.-M. Morel
(\texttt{jean-michel.morel@cmla.ens-cachan.fr}) are with the \emph{Centre de
math\'ematiques et de leurs applications} (CMLA), \'Ecole Normale Sup\'eriore
de Cachan, 61 Av. du Pr\'esident Wilson, F-94230 Cachan, France}}

\markboth{IEEE Transactions of Image Processing,~Vol.~X, No.~X, Month~2015}%
{Arias, Morel: A Non-local Bayesian Video Denoising Method}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	video denoising, Bayesian methods, patch-based methods
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\begin{figure}[htpb!]
	\centering
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
%	\vspace{.1cm}
	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
	the 20 nearest neighbors (top), the corresponding MAP estimates (middle) and the sample mean 
	and first 19 principal directions computed from the sample covariance matrix (bottom).
	For each image, each column corresponds to the 4 spatial slices of a $9\times9\times4$ patch.}
	\label{fig:patch_groups_patches}
\end{figure}

@@

@@

		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_derf_neg-weights.eps}\\
	\end{center}
	\caption{PSNR averaged over four color sequences, when varying the
		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
		estimate; bottom row: final estimate. From left to right, results for
		$\sigma = 10, 20, 30, 40$.} 
	\label{fig:rank1-nsim1-psnr-color}
\end{figure*}

\begin{figure*}[htpb!]
	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono_neg-vs-pos-weights.eps}\\

@@

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,image_denoising,video_denoising,covariance_estimation}

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[10pt, a4paper]{article}
%
\usepackage{makeidx}  % allows for indexgeneration
%

% allow for compress references ranges
% noadjust removes a leading space before the []
\usepackage[noadjust]{cite}

@@

\usepackage[left=1.0in,right=1.0in]{geometry}
\usepackage{pdflscape}
\usepackage{hyperref}

@@

% pablo's commands for comments and suggested modifications
%\newcommand{\pa}[1]{\textcolor{cyan}{#1}}
\newcommand{\pa}[1]{#1}
\newcommand{\psub}[2]{\pa{\sout{#1}}\pa{/#2}}
\newcommand{\prm}[1]{\pa{\sout{#1}}}
\newcommand{\padd}[1]{\pa{#1}}
%\newcommand{\pcomment}[1]{\textit{\pa{#1}}}
\newcommand{\pcomment}[1]{}

@@

\title{A Non-local Bayesian Video Denoising Method}
\date{}

\author{Pablo~Arias, Jean-Michel~Morel%
\thanks{P. Arias (\texttt{pablo.arias@cmla.ens-cachan.fr}) and J.-M. Morel
(\texttt{jean-michel.morel@cmla.ens-cachan.fr}) are with the \emph{Centre de
math\'ematiques et de leurs applications} (CMLA), \'Ecole Normale Sup\'eriore
de Cachan, 61 Av. du Pr\'esident Wilson, F-94230 Cachan, France}
\\[1ex] CMLA, ENS Cachan}

\makeatletter         
\def\@maketitle{
\raggedright
\begin{center}
	{\huge \bfseries \sffamily \@title }\\[8ex] 
	{\Large \bfseries \sffamily Report for the Project }\\
	\includegraphics[width = 80mm]{Plein-Phare.png}\\[8ex]
	{\Large  \@author}\\[4ex] 
\end{center}}
\makeatother

@@

@@

@@

\begin{figure}[htpb!]
	\centering
%	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}
%	\hfill
%	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}
	\hfill
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}
	\hfill
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
	\vspace{.2cm}
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}
	\hfill
	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
	the 20 nearest neighbors (top), the corresponding MAP estimates (middle) and the sample mean 
	and first 19 principal directions computed from the sample covariance matrix (bottom).
	For each image, each column corresponds to the 4 spatial slices of a $9\times9\times4$ patch.}
	\label{fig:patch_groups_patches}
\end{figure}

@@

		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_derf_neg-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_derf_neg-weights.eps}\\
	\end{center}
	\caption{PSNR averaged over four color sequences, when varying the
		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
		estimate; bottom row: final estimate. From left to right, results for
		$\sigma = 10, 20, 30, 40$.} 
	\label{fig:rank1-nsim1-psnr-color}

	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono_neg-vs-pos-weights.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono_neg-vs-pos-weights.eps}\\

@@

@@

\begin{landscape}

@@

\end{landscape}

@@

\bibliographystyle{plain}
\bibliography{image_denoising,video_denoising,covariance_estimation}
